Understanding Feedback Mechanisms in Machine Learning Jupyter Notebooks

### 2025-03-13 report/emse24-revised.tex
feat: add declaration section to paper

\paragraph{\textbf{Conflict of Interest}} The authors declare that they have no conflict of interest.

\paragraph{\textbf{Data Availability Statement}} The dataset created and used in this study along with the replication package is shared publicly under the Creative Commons Attribution (CC-BY) license: https://doi.org/10.6084/m9.figshare.26372140.v1. The case study candidates analyzed in RQ2 and RQ3 can be viewed in our online appendix: https://arumoy.me/shome2023notebook.

>>>>

\subsection{Funding}
Open access funding provided by Delft University of Technology.

\subsection{Informed Consent}
Not applicable

\subsection{Author Contributions}
\begin{description}
  \item[Arumoy Shome:] Conceptualization and study design. Data collection, processing and analysis. Primary author of manuscript.
  \item[Luis Cruz:] Conceptualization and study design. Data analysis. Review and editing.
  \item[Diomidis Spinellis:] Study design. Review and editing.
  \item[Arie van Deursen:] Review and editing.
\end{description}

\subsection{Data Availability Statement}
The dataset created and used in this study along with the replication package is shared publicly under the Creative Commons Attribution (CC-BY) license: https://doi.org/10.6084/m9.figshare.26372140.v1. The case study candidates analyzed in RQ2 and RQ3 can be viewed in our online appendix: https://arumoy.me/shome2023notebook.

\subsection{Conflict of Interest}
The authors declare that they have no conflict of interest.

\subsection{Clinical Trial Number}
Not applicable
